Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Fix variable labels

score.summary <- melt(ans.summary, measure.vars=20:24, value.name = "Score", variable.name = "Test")
score.summary$Test <- factor(score.summary$Test, levels=c("lineup", "card_rot", "fig_class", "folding", "vis_search"), labels=c("Lineups", "Card Rotation", "Figure~Class.", "Paper Folding", "Visual Search"))
qrange$sqrt.k <- sqrt(qrange$k-1)
qrange$Test <- factor(qrange$testtype, levels=c("lineup", "card_rot", "fig_class", "folding", "vis_search"), labels=c("Lineups", "Card Rotation", "Figure~Class.", "Paper Folding", "Visual Search"))

qr1 <- qrange
qr1$Type <- "Theoretical\nRange"
qr2 <- qrange
qr2$Type <- "Scores\nindicating\nguessing"
qr2$n <- with(qr2, -n/(k-1))

@@

ggplot() + 
  geom_bar(data=qrange, aes(width=.9, x=Test, y=n, fill=Type), alpha=.35, stat="identity", position="identity", colour="red", inherit.aes=F) +
  scale_fill_manual("", values=c(NA, "red")) + 
  geom_boxplot(data=score.summary, aes(x=factor(Test), y=Score), inherit.aes=F, fill="grey") +
  theme_bw()  + 
  ylab("Test Scores") + 
  xlab("") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  theme(plot.margin=unit(c(0,0,0,0),"mm")) + 
  theme(legend.position=c(.85,.825),  legend.box.just = "left", 
        legend.key.height=unit(12, "mm")) 
  #coord_flip()
@
%

>>>>

score.summary <- melt(ans.summary, measure.vars=20:24, value.name = "Score", variable.name = "Test")
score.summary$Test <- factor(score.summary$Test, levels=c("lineup", "card_rot", "fig_class", "folding", "vis_search"), labels=c("Lineups", "Card Rotation", "Figure Class.", "Paper Folding", "Visual Search"))
qrange$sqrt.k <- sqrt(qrange$k-1)
qrange$Test <- factor(qrange$testtype, levels=c("lineup", "card_rot", "fig_class", "folding", "vis_search"), labels=c("Lineups", "Card Rotation", "Figure Class.", "Paper Folding", "Visual Search"))

qr1 <- qrange
qr1$Type <- "Theoretical\nRange"
qr2 <- qrange
qr2$Type <- "Scores indicating\nguessing"
qr2$n <- with(qr2, -n/(k-1))

@@

ggplot() + 
  geom_bar(data=qrange, aes(width=.9, x=Test, y=n, fill=Type), alpha=.35, stat="identity", position="identity", colour="red", inherit.aes=F) +
  scale_fill_manual("", values=c(NA, "red")) + 
  geom_boxplot(data=score.summary, aes(x=factor(Test), y=Score), inherit.aes=F, fill="grey") +
  theme_bw()  + 
  ylab("Test Scores") + 
  xlab("") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  theme(plot.margin=unit(c(0,0,0,0),"mm")) + 
  theme(legend.position=c(.80,.825),  legend.box.just = "left", 
        legend.key.height=unit(8, "mm")) 
  #coord_flip()
@
%
